Title field: summary

### 2021-02-02 inst/examples/title.Rmd
ok
summarytitle-1.png changed

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
p <- top_plot(df, "title", ntop = ntop) +
       scale_y_log10() +
       labs(y = "Entries (n)", title = "Top titles")
print(p)
```

>>>>

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=6, fig.height=4}
library(ggplot2)
p <- top_plot(df, "title", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:
